### 2012-09-03 inst/examples/figure3.Rmd
figure 3 more reps

``` {r  echo=FALSE, cache=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````

@@

 Implements a numerical version of the SDP described in `r knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
 Compute the optimal solution under different forms of uncertainty.

@@

ggplot(policy) + geom_line(aes(stock, stock-x_grid[value], color=variable))

linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,150, length=20)), by=variable]
ggplot(linear) + geom_line(aes(x,y,color=variable))
#  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
	#geom_smooth(aes(stock, stock-x_grid[value], color=variable)) 
```

>>>>

``` {r  echo=FALSE, cache=FALSE }
#opts_knit$set(upload.fun = socialR::flickr.url)
#options(device = function(width = 5, height = 5) {
#    pdf(NULL, width = width, height = height)
#})
````

@@

 Implements a numerical version of the SDP described in `r #knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
 Compute the optimal solution under different forms of uncertainty.

@@

ggplot(policy) + geom_line(aes(stock, stock-x_grid[value], color=variable))
dt <- data.table(policy)
linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,150, length=20)), by=variable]
ggplot(linear) + geom_line(aes(x,y,color=variable))
#  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
	#geom_smooth(aes(stock, stock-x_grid[value], color=variable)) 
```
